---
title: "Abacavirinol Males"
author: "Bridget East"
date: "11/26/18"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
abac <-read.csv(file="abacavirinol.csv",header=TRUE)
Male <- filter(abac,sex=="M")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->
  
A new  preventative aides medictaion (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation.
  
Finish this!
  
There are 4,927 people involved in this study, and 5 variables were observed. Those five variables were type of treatment, sex, whether or not they got infected with the HIV virus, whether or not they are IV drug users, and whether or not they belong to the LGBT community. From this study of 4,927 participants, 2,289 were male and 2,638 were female. 601 participants were LGBT, while 707 used IV drugs. This study was similair to the RV144 rial done in Thailand in 2009.
  
# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
  
For this project we are going to observe the results of the study from only the male participants. We will look at graphical results using barchartGC, numerical results using colPerc and rowPerc, and inferential results using chisqtestGC,and fisher.test and I will explain all of the results from each individual R block.
  
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
  
There are three types of results in this section for us to observe; Graphical, Numerical, and Inferential.
  
## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
   
```{r}
maleresults<-xtabs(~infected+treatment,data=Male)
barchartGC(maleresults,type = "percent")
```
   
This is a bar chart that shows the treatments used and the percent of males who were infected with aids and those who were not. It looks as though more males infected had taken the placebo than those who took the drug. It looks like there is almost a forty percent difference between the different types of treatments.
   
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
colPerc(maleresults)
rowPerc(maleresults)
```
  
According to the numerical results, four percent of males who took the drug were infected, while eight percent who took the placebo were infected. So it looks as if the medication was slightly effective according to colPerc. Going off of rowPerc, thirty percent that were affected took the drug and almost 70 percent that were affected took the placebo, the medication looks very effective.
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
chisqtestGC(maleresults, graph = TRUE)
```
  
```{r}
fisher.test(maleresults)
```
 
The null hypothesis is that there is no significant difference between specified populations, any observed difference is being due to sampling or experimental error.
We reject the null hypothesis, p-value is extremely low. So for males in general the drug didnt have an effect on HIV virus.
  
  

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
